---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README_figures/README-",
  fig.retina = 2
)
```

# lato

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![BSD License](https://img.shields.io/badge/license-MIT-brightgreen.svg)](https://opensource.org/licenses/MIT)

**This package is in early development. It probably will not work well for you.**

It will also be re-named.


## Installation

This package is not ready for [CRAN](http://cran.r-project.org/) just yet, but you can use [devtools](http://cran.r-project.org/web/packages/devtools/index.html) to be wild and install install the latest and greatest development version. To do so:                           

```{r installation, eval=FALSE}                                                            
if(!require("devtools")) install.packages("devtools")
devtools::install_github("briandconnelly/lato") 
```


## Example

```{r mtcars_example, message=FALSE}
library(ggplot2)
library(lato)

p1 <- ggplot(mtcars, aes(wt, mpg, color = as.factor(cyl) )) +
    facet_grid(cyl ~ .) +
    geom_line() +
    geom_point() +
    scale_color_hue(name = "# Cylinders") +
    labs(
        x = "Weight (tons)",
        y = "Fuel Efficiency (mpg)",
        title = "Just Buy a Convertible",
        subtitle = "Lighter cars are more efficient. Shave off some weight by\nditching the roof, and drive your savings to the bank!",
        caption = "Source: Motor Trend"
    ) +
    theme_lato()

p1
```

### Dark Mode

```{r mtcars_dark, message=FALSE, warning=FALSE}
p1 + theme_lato_dark()
```

## Contributer Code of Conduct

This project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

